Measurement Bias from Address Aliasing

### 2016-01-10 paper.tex
Changed the author layout and added anonymous option.

\author{\IEEEauthorblockN{Lars Kirkholt Melhus, Rune Erlend Jensen}
\IEEEauthorblockA{Dept. of Computer and Information Science (IDI)\\
NTNU, Norway\\
lars.kirkholt.melhus@gmail.com, runeerle@idi.ntnu.no}
}

\date{19 November 2014}

>>>>

\iftrue
\author{\IEEEauthorblockN{Lars Kirkholt Melhus}
\IEEEauthorblockA{Dept. of Computer and Information Science (IDI)\\
NTNU, Norway\\
lars.kirkholt.melhus@gmail.com}
\and
\IEEEauthorblockN{Rune Erlend Jensen}
\IEEEauthorblockA{Dept. of Computer and Information Science (IDI)\\
NTNU, Norway\\
runeerle@idi.ntnu.no}
}
\else
\author{\IEEEauthorblockN{Anonymous}
\IEEEauthorblockA{Organization\\
University\\
anonymous@mail.com}
\and
\IEEEauthorblockN{Anonymous}
\IEEEauthorblockA{Organization\\
University\\
anonymous@mail.com}
}

\fi

\date{10 January 2016}
